---
output: 
  flexdashboard::flex_dashboard
---

<style type="text/css">
.value-box .value {
  color: white;
  font-size: 30px;
}
.value-box .caption {
  color: white;
  margin-bottom: 0px;
}
.chart-title {
  background: black;
  color: white;
  font-weight: bold;
  font-size: 16px
}
.chart-stage-flex {
  overflow: scroll !important;
}
.datatables{
    overflow: auto;
}
.header-text {
  background: black;
  color: white;
  font-weight: bold;
  font-size: 16px;
  padding: 7px 10px 0px;
}
.section.sidebar {
  left: 0;
  bottom: 0;
  padding-top: 10px;
  padding-bottom: 10px;
  padding-left: 20px;
  padding-right: 10px;
}

.highlight-text {
  background: #2780E3;
  color: white;
}
</style>



---
title: '`r paste0(run, ": ", sample, " | ", tumor, " | ", panel)`'
---

```{r main, child = paste0("sampleReport_Main.Rmd")}
```

```{r snvindel, child = paste0("sampleReport_SmallVariant.Rmd"), eval = is_vars}
```


```{r cna, child = paste0("sampleReport_CNA.Rmd"), eval = is_cna_gene}
```


```{r fusion, child = paste0("sampleReport_Fusion.Rmd"), eval = is_fusion}
```


```{r splicing, child = paste0("sampleReport_Splicing.Rmd"), eval = is_splicing}
```


```{r tmb, child = paste0("sampleReport_TMB.Rmd"), eval = is_tmb}
```


```{r msi, child = paste0("sampleReport_MSI.Rmd"), eval = is_msi}
```


```{r sampleqc, child = paste0("sampleReport_QC.Rmd")}
```

